---
title: "R Notebook"
output: html_notebook
---
[Databricks Connect for R](https://learn.microsoft.com/en-us/azure/databricks/dev-tools/databricks-connect/r/) 
### This can be set for every RStudio instead of running every time

needs packages 
Tools>Install from CRAN  

sparklyr,pysparklyr,reticulate,usethis,dplyr,dbplyr 
>> install.packages(c("sparklyr", "pysparklyr", "reticulate", "usethis", "dplyr", "dbplyr"))


then in console  

reticulate::install_python(version = "3.10")

# Please add your Host to 'DATABRICKS_HOST' inside your .Renviron file.
[databricks connetion for Rstudio](https://support.posit.co/hc/en-us/articles/115010915687-Using-RStudio-Connections-in-the-RStudio-I)
cluster_id="0613-222509-q2qkl4bq"
pysparklyr::install_databricks(cluster_id = "0613-222509-q2qkl4bq")

```{python}

```


```{r}
library(sparklyr)

sc <- spark_connect(
  cluster_id = "0613-222509-q2qkl4bq",
  method = "databricks_connect"
)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
```{r}
library(dplyr)
library(dbplyr)

# Read samples.nyctaxi.trips table with catalog.schema.table heirarchy
trips <- tbl(sc, in_catalog("samples", "nyctaxi", "trips"))
trips
```

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
